### 2015-06-11 ApresentacoesArtigos/quali/quali.tex
adiantada introdução

\section{Literature review}
The field  of complex networks is relatively new ($\approx 25$ years)
and literature presents diverging definitions for the field itself.
One definition that is having increasing acceptance
considers a complex network a ``large graph with non-trivial topological features''.
This definition is misleading in at least two points: there are networks of interest with trivial topological features, such as the paradigmatic Erdös-Rényi network and the lattice network~\cite{newman}. 
Second, it fails to deliver the fundamental message that the complex network is not an isolated mathematical graph structure. Complex networks of interest are real networks or idealized models for understanding them. Besides that, not only large graphs are of interest, but small graphs are very often used as toy examples and measured as extension of larger structures.
A definition, still far from perfect, but preferred in this work, is:
%``often large graphs considered in the physical
%or natural environment they reside''.
``often large and non-trivial graphs considered in,
or for the consideration of, 
the environment they reside''.
This definition resolves both issues.

@@

A careful consideration of the books and articles read for this research
is given in Section~\ref{}.

>>>>

\section{Literature review}
A área das redes complexas é relativamente nova ($\approx 25$ anos)
e a literatura apresenta definições divergentes da área em si.
Uma definição que tem ti

One definition that is having increasing acceptance
considers a complex network a ``large graph with non-trivial topological features''.
This definition is misleading in at least two points: there are networks of interest with trivial topological features, such as the paradigmatic Erdös-Rényi network and the lattice network~\cite{newman}. 
Second, it fails to deliver the fundamental message that the complex network is not an isolated mathematical graph structure. Complex networks of interest are real networks or idealized models for understanding them. Besides that, not only large graphs are of interest, but small graphs are very often used as toy examples and measured as extension of larger structures.
A definition, still far from perfect, but preferred in this work, is:
%``often large graphs considered in the physical
%or natural environment they reside''.
``often large and non-trivial graphs considered in,
or for the consideration of, 
the environment they reside''.
This definition resolves both issues.

@@

A careful consideration of the books and articles read for this research
is given in Section~\ref{}.
\subsection{Ambiguidades e sinonimos no jargão}
